### 2023-09-01 preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@5012201741ab7f7cf3b29d541c45d898fad9f315 🚀

For all bat hosts of \emph{Betacoronavirus}, we extracted their
predicted viral sharing network, generated from a previously published
generalized additive mixed model of virus sharing by a tensor function
of phylogenetic distance and geographic range overlap across
mammals.\textsuperscript{\textbf{Albery2020PreGlo?}} This network stores
pairwise values of viral community similarity, measured for all hosts
(to maintain consistency with teh phylogenetic diversity measure) across
all viruses; therefore, we consider that it accounts for some overall
similarity in the way hosts deal with viruses, and not only
betacoronaviruses. There is empirical evidence that capacity for
cross-species transmission even between divergent species is generally
high,\textsuperscript{53} especially for
beta-coronaviruses.\textsuperscript{13} To project viral sharing values
into a single value for every pixel, we averaged the pairwise scores.
High values of the average sharing propensity means that this specific
extant bat assemblage is likely to be proficient at exchanging viruses.

@@

\leavevmode\hypertarget{ref-Agosta2010How}{}%
\CSLLeftMargin{2. }
\CSLRightInline{Agosta, S. J., Janz, N. \& Brooks, D. R. How specialists
can be generalists: Resolving the {`parasite paradox'} and implications
for emerging infectious disease. \emph{Zoologia (Curitiba)} \textbf{27},
151--162 (2010).}

\leavevmode\hypertarget{ref-Power2004Pathogen}{}%
\CSLLeftMargin{3. }
\CSLRightInline{Power, A. G. \& Mitchell, C. E. Pathogen Spillover in
Disease Epidemics. \emph{The American Naturalist} \textbf{164}, S79--S89
(2004).}

\leavevmode\hypertarget{ref-Geoghegan2017Comparative}{}%
\CSLLeftMargin{4. }
\CSLRightInline{Geoghegan, J. L., Duchêne, S. \& Holmes, E. C.
Comparative analysis estimates the relative frequencies of co-divergence
and cross-species transmission within viral families. \emph{PLOS
Pathogens} \textbf{13}, e1006215 (2017).}

\leavevmode\hypertarget{ref-Thompson2005Geographic}{}%
\CSLLeftMargin{5. }
\CSLRightInline{Thompson, J. N. \emph{The Geographic Mosaic of
Coevolution}. (University Of Chicago Press, 2005).}

\leavevmode\hypertarget{ref-Thompson1994Coevolutionary}{}%
\CSLLeftMargin{6. }
\CSLRightInline{Thompson, J. N. \emph{The Coevolutionary Process}.
(University of Chicago Press, 1994).}

\leavevmode\hypertarget{ref-Janzen1980When}{}%
\CSLLeftMargin{7. }
\CSLRightInline{Janzen, D. H. When is it Coevolution? \emph{Evolution}
\textbf{34}, 611--612 (1980).}

\leavevmode\hypertarget{ref-Price2002Macroevolutionary}{}%
\CSLLeftMargin{8. }
\CSLRightInline{Price, P. W. \emph{Macroevolutionary Theory on
Macroecological Patterns}. (Cambridge University Press, 2002).
doi:\href{https://doi.org/10.1017/CBO9780511615030}{10.1017/CBO9780511615030}.}

\leavevmode\hypertarget{ref-Gomulkiewicz2007Dos}{}%
\CSLLeftMargin{9. }
\CSLRightInline{Gomulkiewicz, R. \emph{et al.} Dos and don'ts of testing
the geographic mosaic theory of coevolution. \emph{Heredity}
\textbf{98}, 249--258 (2007).}

\leavevmode\hypertarget{ref-Thrall2007Coevolution}{}%
\CSLLeftMargin{10. }
\CSLRightInline{Thrall, P. H., Hochberg, M. E., Burdon, J. J. \& Bever,
J. D. Coevolution of symbiotic mutualists and parasites in a community
context. \emph{Trends in Ecology \& Evolution} \textbf{22}, 120--126
(2007).}

\leavevmode\hypertarget{ref-Anthony2017Global}{}%
\CSLLeftMargin{11. }
\CSLRightInline{Anthony, S. J. \emph{et al.} Global patterns in
coronavirus diversity. \emph{Virus Evolution} \textbf{3}, (2017).}

\leavevmode\hypertarget{ref-Ruiz-Aravena2022Ecology}{}%
\CSLLeftMargin{12. }
\CSLRightInline{Ruiz-Aravena, M. \emph{et al.} Ecology, evolution and
spillover of coronaviruses from bats. \emph{Nature Reviews Microbiology}
\textbf{20}, 299--314 (2022).}

\leavevmode\hypertarget{ref-Latinne2020Origin}{}%
\CSLLeftMargin{13. }
\CSLRightInline{Latinne, A. \emph{et al.} Origin and cross-species
transmission of bat coronaviruses in China. \emph{bioRxiv: The Preprint
Server for Biology} 2020.05.31.116061 (2020)
doi:\href{https://doi.org/10.1101/2020.05.31.116061}{10.1101/2020.05.31.116061}.}

\leavevmode\hypertarget{ref-Anthony2013Coronaviruses}{}%
\CSLLeftMargin{14. }
\CSLRightInline{Anthony, S. J. \emph{et al.} Coronaviruses in bats from
Mexico. \emph{The Journal of General Virology} \textbf{94}, 1028--1038
(2013).}

\leavevmode\hypertarget{ref-Goes2013Novel}{}%
\CSLLeftMargin{15. }
\CSLRightInline{Góes, L. G. B. \emph{et al.} Novel Bat Coronaviruses,
Brazil and Mexico. \emph{Emerging Infectious Diseases} \textbf{19},
1711--1713 (2013).}

\leavevmode\hypertarget{ref-Goes2016Genetic}{}%
\CSLLeftMargin{16. }
\CSLRightInline{Góes, L. G. B. \emph{et al.} Genetic diversity of bats
coronaviruses in the Atlantic Forest hotspot biome, Brazil.
\emph{Infection, Genetics and Evolution: Journal of Molecular
Epidemiology and Evolutionary Genetics in Infectious Diseases}
\textbf{44}, 510--513 (2016).}

\leavevmode\hypertarget{ref-Brandao2008Coronavirus}{}%
\CSLLeftMargin{17. }
\CSLRightInline{Brandão, P. E. \emph{et al.} A coronavirus detected in
the vampire bat Desmodus rotundus. \emph{Brazilian Journal of Infectious
Diseases} \textbf{12}, 466--468 (2008).}

\leavevmode\hypertarget{ref-Tanalgo2022Mapping}{}%
\CSLLeftMargin{18. }
\CSLRightInline{Tanalgo, K. C., Oliveira, H. F. M. \& Hughes, A. C.
Mapping global conservation priorities and habitat vulnerabilities for
cave-dwelling bats in a changing world. \emph{Science of The Total
Environment} \textbf{843}, 156909 (2022).}

\leavevmode\hypertarget{ref-Olival2017Host}{}%
\CSLLeftMargin{19. }
\CSLRightInline{Olival, K. J. \emph{et al.} Host and viral traits
predict zoonotic spillover from mammals. \emph{Nature} \textbf{546},
646--650 (2017).}

\leavevmode\hypertarget{ref-Becker2022Optimising}{}%
\CSLLeftMargin{20. }
\CSLRightInline{Becker, D. J. \emph{et al.} Optimising predictive models
to prioritise viral discovery in zoonotic reservoirs. \emph{The Lancet
Microbe} (2022)
doi:\href{https://doi.org/10.1016/S2666-5247(21)00245-7}{10.1016/S2666-5247(21)00245-7}.}

\leavevmode\hypertarget{ref-Worobey2022Huanan}{}%
\CSLLeftMargin{21. }
\CSLRightInline{Worobey, M. \emph{et al.} The Huanan market was the
epicenter of SARS-CoV-2 emergence. \emph{Zenodo} (2022)
doi:\href{https://doi.org/10.5281/zenodo.6299600}{10.5281/zenodo.6299600}.}

\leavevmode\hypertarget{ref-Temmam2022Bat}{}%
\CSLLeftMargin{22. }
\CSLRightInline{Temmam, S. \emph{et al.} Bat coronaviruses related to
SARS-CoV-2 and infectious for human cells. \emph{Nature} \textbf{604},
330--336 (2022).}

\leavevmode\hypertarget{ref-Boni2020Evolutionary}{}%
\CSLLeftMargin{23. }
\CSLRightInline{Boni, M. F. \emph{et al.} Evolutionary origins of the
SARS-CoV-2 sarbecovirus lineage responsible for the COVID-19 pandemic.
\emph{Nature microbiology} \textbf{5}, 1408--1417 (2020).}

\leavevmode\hypertarget{ref-Cohen2022Sampling}{}%
\CSLLeftMargin{24. }
\CSLRightInline{Cohen, L. E., Fagre, A. C., Chen, B., Carlson, C. J. \&
Becker, D. J. Sampling strategies and pre-pandemic surveillance gaps for
bat coronaviruses. 2022.06.15.496296 (2022)
doi:\href{https://doi.org/10.1101/2022.06.15.496296}{10.1101/2022.06.15.496296}.}

\leavevmode\hypertarget{ref-Olival2020Possibility}{}%
\CSLLeftMargin{25. }
\CSLRightInline{Olival, K. J. \emph{et al.} Possibility for reverse
zoonotic transmission of SARS-CoV-2 to free-ranging wildlife: A case
study of bats. \emph{PLoS pathogens} \textbf{16}, e1008758 (2020).}

\leavevmode\hypertarget{ref-Ammerman2012First}{}%
\CSLLeftMargin{26. }
\CSLRightInline{Ammerman, L. K., Lee, D. N. \& Tipps, T. M. First
molecular phylogenetic insights into the evolution of free-tailed bats
in the subfamily Molossinae (Molossidae, Chiroptera). \emph{Journal of
Mammalogy} \textbf{93}, 12--28 (2012).}

\leavevmode\hypertarget{ref-Banerjee2020Novel}{}%
\CSLLeftMargin{27. }
\CSLRightInline{Banerjee, A. \emph{et al.} Novel Insights Into Immune
Systems of Bats. \emph{Frontiers in Immunology} \textbf{11}, 26 (2020).}

\leavevmode\hypertarget{ref-Shi2014Deep}{}%
\CSLLeftMargin{28. }
\CSLRightInline{Shi, J. J. \emph{et al.} A Deep Divergence Time between
Sister Species of Eidolon (Pteropodidae) with Evidence for Widespread
Panmixia. \emph{Acta Chiropterologica} \textbf{16}, 279--292 (2014).}

\leavevmode\hypertarget{ref-Kettenburg2022Full}{}%
\CSLLeftMargin{29. }
\CSLRightInline{Kettenburg, G. \emph{et al.} Full Genome Nobecovirus
Sequences From Malagasy Fruit Bats Define a Unique Evolutionary History
for This Coronavirus Clade. \emph{Frontiers in Public Health}
\textbf{10}, (2022).}

\leavevmode\hypertarget{ref-Rulli2021Landuse}{}%
\CSLLeftMargin{30. }
\CSLRightInline{Rulli, M. C., D'Odorico, P., Galli, N. \& Hayman, D. T.
Land-use change and the livestock revolution increase the risk of
zoonotic coronavirus transmission from rhinolophid bats. \emph{Nature
Food} \textbf{2}, 409--416 (2021).}

\leavevmode\hypertarget{ref-Cui2019Origin}{}%
\CSLLeftMargin{31. }
\CSLRightInline{Cui, J., Li, F. \& Shi, Z.-L. Origin and evolution of
pathogenic coronaviruses. \emph{Nature Reviews Microbiology}
\textbf{17}, 181--192 (2019).}

\leavevmode\hypertarget{ref-Muylaert2022Present}{}%
\CSLLeftMargin{32. }
\CSLRightInline{Muylaert, R. L. \emph{et al.} Present and future
distribution of bat hosts of sarbecoviruses: Implications for
conservation and public health. \emph{Proceedings of the Royal Society
B: Biological Sciences} \textbf{289}, 20220397 (2022).}

\leavevmode\hypertarget{ref-Hassell2017Urbanization}{}%
\CSLLeftMargin{33. }
\CSLRightInline{Hassell, J. M., Begon, M., Ward, M. J. \& Fèvre, E. M.
Urbanization and disease emergence: Dynamics at the
wildlife--livestock--human interface. \emph{Trends in ecology \&
evolution} \textbf{32}, 55--67 (2017).}

\leavevmode\hypertarget{ref-Hu2017Discovery}{}%
\CSLLeftMargin{34. }
\CSLRightInline{Hu, B. \emph{et al.} Discovery of a rich gene pool of
bat SARS-related coronaviruses provides new insights into the origin of
SARS coronavirus. \emph{PLoS pathogens} \textbf{13}, e1006698 (2017).}

\leavevmode\hypertarget{ref-Wang2018Serological}{}%
\CSLLeftMargin{35. }
\CSLRightInline{Wang, N. \emph{et al.} Serological Evidence of Bat
SARS-Related Coronavirus Infection in Humans, China. \emph{Virologica
Sinica} \textbf{33}, 104--107 (2018).}

\leavevmode\hypertarget{ref-Muller2014Mers}{}%
\CSLLeftMargin{36. }
\CSLRightInline{Müller, M. A. \emph{et al.} MERS coronavirus
neutralizing antibodies in camels, Eastern Africa, 1983--1997.
\emph{Emerging infectious diseases} \textbf{20}, 2093 (2014).}

\leavevmode\hypertarget{ref-Xu2004Epidemiologic}{}%
\CSLLeftMargin{37. }
\CSLRightInline{Xu, R.-H. \emph{et al.} Epidemiologic Clues to SARS
Origin in China. \emph{Emerging Infectious Diseases} \textbf{10},
1030--1037 (2004).}

\leavevmode\hypertarget{ref-Kasso2013Ecological}{}%
\CSLLeftMargin{38. }
\CSLRightInline{Kasso, M. \& Balakrishnan, M. Ecological and Economic
Importance of Bats (Order Chiroptera). \emph{ISRN Biodiversity}
\textbf{2013}, e187415 (2013).}

\leavevmode\hypertarget{ref-Voigt2016Bats}{}%
\CSLLeftMargin{39. }
\CSLRightInline{\emph{Bats in the Anthropocene: Conservation of Bats in
a Changing World}. (Springer International Publishing, 2016).
doi:\href{https://doi.org/10.1007/978-3-319-25220-9}{10.1007/978-3-319-25220-9}.}

\leavevmode\hypertarget{ref-Williams-Guillen2008Bats}{}%
\CSLLeftMargin{40. }
\CSLRightInline{Williams-Guillén, K., Perfecto, I. \& Vandermeer, J.
Bats Limit Insects in a Neotropical Agroforestry System. \emph{Science}
\textbf{320}, 70--70 (2008).}

\leavevmode\hypertarget{ref-Gonsalves2013Mosquito}{}%
\CSLLeftMargin{41. }
\CSLRightInline{Gonsalves, L., Bicknell, B., Law, B., Webb, C. \&
Monamy, V. Mosquito Consumption by Insectivorous Bats: Does Size Matter?
\emph{PLOS ONE} \textbf{8}, e77183 (2013).}

\leavevmode\hypertarget{ref-Gonsalves2013Mosquitoes}{}%
\CSLLeftMargin{42. }
\CSLRightInline{Gonsalves, L., Lamb, S., Webb, C., Law, B. \& Monamy, V.
Do mosquitoes influence bat activity in coastal habitats? \emph{Wildlife
Research} \textbf{40}, 10--24 (2013).}

\leavevmode\hypertarget{ref-Mello2011Missing}{}%
\CSLLeftMargin{43. }
\CSLRightInline{Mello, M. A. R. \emph{et al.} The Missing Part of Seed
Dispersal Networks: Structure and Robustness of Bat-Fruit Interactions.
\emph{PLOS ONE} \textbf{6}, e17395 (2011).}

\leavevmode\hypertarget{ref-Caraballo2022Crossspecies}{}%
\CSLLeftMargin{44. }
\CSLRightInline{Caraballo, D. A. Cross-Species Transmission of Bat
Coronaviruses in the Americas: Contrasting Patterns between
Alphacoronavirus and Betacoronavirus. \emph{Microbiology Spectrum}
\textbf{0}, e01411--22 (2022).}

\leavevmode\hypertarget{ref-Wu2021Comprehensive}{}%
\CSLLeftMargin{45. }
\CSLRightInline{Wu, Z. \emph{et al.} \emph{A comprehensive survey of bat
sarbecoviruses across China for the origin tracing of SARS-CoV and
SARS-CoV-2}. (2021)
doi:\href{https://doi.org/10.21203/rs.3.rs-885194/v1}{10.21203/rs.3.rs-885194/v1}.}

\leavevmode\hypertarget{ref-Carlson2022Climate}{}%
\CSLLeftMargin{46. }
\CSLRightInline{Carlson, C. J. \emph{et al.} Climate change increases
cross-species viral transmission risk. \emph{Nature} 1--1 (2022)
doi:\href{https://doi.org/10.1038/s41586-022-04788-w}{10.1038/s41586-022-04788-w}.}

\leavevmode\hypertarget{ref-Alves2018Geographic}{}%
\CSLLeftMargin{47. }
\CSLRightInline{Alves, D. M. C. C., Diniz-Filho, J. A. F., da Silva e
Souza, K., Gouveia, S. F. \& Villalobos, F. Geographic variation in the
relationship between large-scale environmental determinants and bat
species richness. \emph{Basic and Applied Ecology} \textbf{27}, 1--8
(2018).}

\leavevmode\hypertarget{ref-Treitler2016Effect}{}%
\CSLLeftMargin{48. }
\CSLRightInline{Treitler, J. T., Heim, O., Tschapka, M. \& Jung, K. The
effect of local land use and loss of forests on bats and nocturnal
insects. \emph{Ecology and Evolution} \textbf{6}, 4289--4297 (2016).}

\leavevmode\hypertarget{ref-Mendenhall2014Predictinga}{}%
\CSLLeftMargin{49. }
\CSLRightInline{Mendenhall, C. D., Karp, D. S., Meyer, C. F. J., Hadly,
E. A. \& Daily, G. C. Predicting biodiversity change and averting
collapse in agricultural landscapes. \emph{Nature} \textbf{509},
213--217 (2014).}

>>>>

For all bat hosts of \emph{Betacoronavirus}, we extracted their
predicted viral sharing network, generated from a previously published
generalized additive mixed model of virus sharing by a tensor function
of phylogenetic distance and geographic range overlap across
mammals.\textsuperscript{\textbf{Albery2020PreGlo?}} This network stores
pairwise values of viral community similarity, measured for all hosts
(to maintain consistency with teh phylogenetic diversity measure) across
all viruses; therefore, we consider that it accounts for some overall
similarity in the way hosts deal with viruses, and not only
betacoronaviruses. There is empirical evidence that capacity for
cross-species transmission even between divergent species is generally
high,\textsuperscript{55} especially for
beta-coronaviruses.\textsuperscript{14} To project viral sharing values
into a single value for every pixel, we averaged the pairwise scores.
High values of the average sharing propensity means that this specific
extant bat assemblage is likely to be proficient at exchanging viruses.

@@

\leavevmode\hypertarget{ref-Anthony2017Global}{}%
\CSLLeftMargin{2. }
\CSLRightInline{Anthony, S. J. \emph{et al.} Global patterns in
coronavirus diversity. \emph{Virus Evolution} \textbf{3}, (2017).}

\leavevmode\hypertarget{ref-Sanchez2022Strategy}{}%
\CSLLeftMargin{3. }
\CSLRightInline{Sánchez, C. A. \emph{et al.} A strategy to assess
spillover risk of bat SARS-related coronaviruses in southeast asia.
\emph{Nature Communications} \textbf{13}, (2022).}

\leavevmode\hypertarget{ref-Agosta2010How}{}%
\CSLLeftMargin{4. }
\CSLRightInline{Agosta, S. J., Janz, N. \& Brooks, D. R. How specialists
can be generalists: Resolving the {`parasite paradox'} and implications
for emerging infectious disease. \emph{Zoologia (Curitiba)} \textbf{27},
151--162 (2010).}

\leavevmode\hypertarget{ref-Power2004Pathogen}{}%
\CSLLeftMargin{5. }
\CSLRightInline{Power, A. G. \& Mitchell, C. E. Pathogen Spillover in
Disease Epidemics. \emph{The American Naturalist} \textbf{164}, S79--S89
(2004).}

\leavevmode\hypertarget{ref-Geoghegan2017Comparative}{}%
\CSLLeftMargin{6. }
\CSLRightInline{Geoghegan, J. L., Duchêne, S. \& Holmes, E. C.
Comparative analysis estimates the relative frequencies of co-divergence
and cross-species transmission within viral families. \emph{PLOS
Pathogens} \textbf{13}, e1006215 (2017).}

\leavevmode\hypertarget{ref-Thompson2005Geographic}{}%
\CSLLeftMargin{7. }
\CSLRightInline{Thompson, J. N. \emph{The Geographic Mosaic of
Coevolution}. (University Of Chicago Press, 2005).}

\leavevmode\hypertarget{ref-Thompson1994Coevolutionary}{}%
\CSLLeftMargin{8. }
\CSLRightInline{Thompson, J. N. \emph{The Coevolutionary Process}.
(University of Chicago Press, 1994).}

\leavevmode\hypertarget{ref-Janzen1980When}{}%
\CSLLeftMargin{9. }
\CSLRightInline{Janzen, D. H. When is it Coevolution? \emph{Evolution}
\textbf{34}, 611--612 (1980).}

\leavevmode\hypertarget{ref-Price2002Macroevolutionary}{}%
\CSLLeftMargin{10. }
\CSLRightInline{Price, P. W. \emph{Macroevolutionary Theory on
Macroecological Patterns}. (Cambridge University Press, 2002).
doi:\href{https://doi.org/10.1017/CBO9780511615030}{10.1017/CBO9780511615030}.}

\leavevmode\hypertarget{ref-Gomulkiewicz2007Dos}{}%
\CSLLeftMargin{11. }
\CSLRightInline{Gomulkiewicz, R. \emph{et al.} Dos and don'ts of testing
the geographic mosaic theory of coevolution. \emph{Heredity}
\textbf{98}, 249--258 (2007).}

\leavevmode\hypertarget{ref-Thrall2007Coevolution}{}%
\CSLLeftMargin{12. }
\CSLRightInline{Thrall, P. H., Hochberg, M. E., Burdon, J. J. \& Bever,
J. D. Coevolution of symbiotic mutualists and parasites in a community
context. \emph{Trends in Ecology \& Evolution} \textbf{22}, 120--126
(2007).}

\leavevmode\hypertarget{ref-Ruiz-Aravena2022Ecology}{}%
\CSLLeftMargin{13. }
\CSLRightInline{Ruiz-Aravena, M. \emph{et al.} Ecology, evolution and
spillover of coronaviruses from bats. \emph{Nature Reviews Microbiology}
\textbf{20}, 299--314 (2022).}

\leavevmode\hypertarget{ref-Latinne2020Origin}{}%
\CSLLeftMargin{14. }
\CSLRightInline{Latinne, A. \emph{et al.} Origin and cross-species
transmission of bat coronaviruses in China. \emph{bioRxiv: The Preprint
Server for Biology} 2020.05.31.116061 (2020)
doi:\href{https://doi.org/10.1101/2020.05.31.116061}{10.1101/2020.05.31.116061}.}

\leavevmode\hypertarget{ref-Anthony2013Coronaviruses}{}%
\CSLLeftMargin{15. }
\CSLRightInline{Anthony, S. J. \emph{et al.} Coronaviruses in bats from
Mexico. \emph{The Journal of General Virology} \textbf{94}, 1028--1038
(2013).}

\leavevmode\hypertarget{ref-Goes2013Novel}{}%
\CSLLeftMargin{16. }
\CSLRightInline{Góes, L. G. B. \emph{et al.} Novel Bat Coronaviruses,
Brazil and Mexico. \emph{Emerging Infectious Diseases} \textbf{19},
1711--1713 (2013).}

\leavevmode\hypertarget{ref-Goes2016Genetic}{}%
\CSLLeftMargin{17. }
\CSLRightInline{Góes, L. G. B. \emph{et al.} Genetic diversity of bats
coronaviruses in the Atlantic Forest hotspot biome, Brazil.
\emph{Infection, Genetics and Evolution: Journal of Molecular
Epidemiology and Evolutionary Genetics in Infectious Diseases}
\textbf{44}, 510--513 (2016).}

\leavevmode\hypertarget{ref-Brandao2008Coronavirus}{}%
\CSLLeftMargin{18. }
\CSLRightInline{Brandão, P. E. \emph{et al.} A coronavirus detected in
the vampire bat Desmodus rotundus. \emph{Brazilian Journal of Infectious
Diseases} \textbf{12}, 466--468 (2008).}

\leavevmode\hypertarget{ref-Tanalgo2022Mapping}{}%
\CSLLeftMargin{19. }
\CSLRightInline{Tanalgo, K. C., Oliveira, H. F. M. \& Hughes, A. C.
Mapping global conservation priorities and habitat vulnerabilities for
cave-dwelling bats in a changing world. \emph{Science of The Total
Environment} \textbf{843}, 156909 (2022).}

\leavevmode\hypertarget{ref-Olival2017Host}{}%
\CSLLeftMargin{20. }
\CSLRightInline{Olival, K. J. \emph{et al.} Host and viral traits
predict zoonotic spillover from mammals. \emph{Nature} \textbf{546},
646--650 (2017).}

\leavevmode\hypertarget{ref-Becker2022Optimising}{}%
\CSLLeftMargin{21. }
\CSLRightInline{Becker, D. J. \emph{et al.} Optimising predictive models
to prioritise viral discovery in zoonotic reservoirs. \emph{The Lancet
Microbe} (2022)
doi:\href{https://doi.org/10.1016/S2666-5247(21)00245-7}{10.1016/S2666-5247(21)00245-7}.}

\leavevmode\hypertarget{ref-Worobey2022Huanan}{}%
\CSLLeftMargin{22. }
\CSLRightInline{Worobey, M. \emph{et al.} The Huanan market was the
epicenter of SARS-CoV-2 emergence. \emph{Zenodo} (2022)
doi:\href{https://doi.org/10.5281/zenodo.6299600}{10.5281/zenodo.6299600}.}

\leavevmode\hypertarget{ref-Temmam2022Bat}{}%
\CSLLeftMargin{23. }
\CSLRightInline{Temmam, S. \emph{et al.} Bat coronaviruses related to
SARS-CoV-2 and infectious for human cells. \emph{Nature} \textbf{604},
330--336 (2022).}

\leavevmode\hypertarget{ref-Boni2020Evolutionary}{}%
\CSLLeftMargin{24. }
\CSLRightInline{Boni, M. F. \emph{et al.} Evolutionary origins of the
SARS-CoV-2 sarbecovirus lineage responsible for the COVID-19 pandemic.
\emph{Nature microbiology} \textbf{5}, 1408--1417 (2020).}

\leavevmode\hypertarget{ref-Cohen2022Sampling}{}%
\CSLLeftMargin{25. }
\CSLRightInline{Cohen, L. E., Fagre, A. C., Chen, B., Carlson, C. J. \&
Becker, D. J. Sampling strategies and pre-pandemic surveillance gaps for
bat coronaviruses. 2022.06.15.496296 (2022)
doi:\href{https://doi.org/10.1101/2022.06.15.496296}{10.1101/2022.06.15.496296}.}

\leavevmode\hypertarget{ref-Olival2020Possibility}{}%
\CSLLeftMargin{26. }
\CSLRightInline{Olival, K. J. \emph{et al.} Possibility for reverse
zoonotic transmission of SARS-CoV-2 to free-ranging wildlife: A case
study of bats. \emph{PLoS pathogens} \textbf{16}, e1008758 (2020).}

\leavevmode\hypertarget{ref-Ammerman2012First}{}%
\CSLLeftMargin{27. }
\CSLRightInline{Ammerman, L. K., Lee, D. N. \& Tipps, T. M. First
molecular phylogenetic insights into the evolution of free-tailed bats
in the subfamily Molossinae (Molossidae, Chiroptera). \emph{Journal of
Mammalogy} \textbf{93}, 12--28 (2012).}

\leavevmode\hypertarget{ref-Banerjee2020Novel}{}%
\CSLLeftMargin{28. }
\CSLRightInline{Banerjee, A. \emph{et al.} Novel Insights Into Immune
Systems of Bats. \emph{Frontiers in Immunology} \textbf{11}, 26 (2020).}

\leavevmode\hypertarget{ref-Shi2014Deep}{}%
\CSLLeftMargin{29. }
\CSLRightInline{Shi, J. J. \emph{et al.} A Deep Divergence Time between
Sister Species of Eidolon (Pteropodidae) with Evidence for Widespread
Panmixia. \emph{Acta Chiropterologica} \textbf{16}, 279--292 (2014).}

\leavevmode\hypertarget{ref-Kettenburg2022Full}{}%
\CSLLeftMargin{30. }
\CSLRightInline{Kettenburg, G. \emph{et al.} Full Genome Nobecovirus
Sequences From Malagasy Fruit Bats Define a Unique Evolutionary History
for This Coronavirus Clade. \emph{Frontiers in Public Health}
\textbf{10}, (2022).}

\leavevmode\hypertarget{ref-Rulli2021Landuse}{}%
\CSLLeftMargin{31. }
\CSLRightInline{Rulli, M. C., D'Odorico, P., Galli, N. \& Hayman, D. T.
Land-use change and the livestock revolution increase the risk of
zoonotic coronavirus transmission from rhinolophid bats. \emph{Nature
Food} \textbf{2}, 409--416 (2021).}

\leavevmode\hypertarget{ref-Cui2019Origin}{}%
\CSLLeftMargin{32. }
\CSLRightInline{Cui, J., Li, F. \& Shi, Z.-L. Origin and evolution of
pathogenic coronaviruses. \emph{Nature Reviews Microbiology}
\textbf{17}, 181--192 (2019).}

\leavevmode\hypertarget{ref-Muylaert2022Present}{}%
\CSLLeftMargin{33. }
\CSLRightInline{Muylaert, R. L. \emph{et al.} Present and future
distribution of bat hosts of sarbecoviruses: Implications for
conservation and public health. \emph{Proceedings of the Royal Society
B: Biological Sciences} \textbf{289}, 20220397 (2022).}

\leavevmode\hypertarget{ref-Hassell2017Urbanization}{}%
\CSLLeftMargin{34. }
\CSLRightInline{Hassell, J. M., Begon, M., Ward, M. J. \& Fèvre, E. M.
Urbanization and disease emergence: Dynamics at the
wildlife--livestock--human interface. \emph{Trends in ecology \&
evolution} \textbf{32}, 55--67 (2017).}

\leavevmode\hypertarget{ref-Hu2017Discovery}{}%
\CSLLeftMargin{35. }
\CSLRightInline{Hu, B. \emph{et al.} Discovery of a rich gene pool of
bat SARS-related coronaviruses provides new insights into the origin of
SARS coronavirus. \emph{PLoS pathogens} \textbf{13}, e1006698 (2017).}

\leavevmode\hypertarget{ref-Wang2018Serological}{}%
\CSLLeftMargin{36. }
\CSLRightInline{Wang, N. \emph{et al.} Serological Evidence of Bat
SARS-Related Coronavirus Infection in Humans, China. \emph{Virologica
Sinica} \textbf{33}, 104--107 (2018).}

\leavevmode\hypertarget{ref-Muller2014Mers}{}%
\CSLLeftMargin{37. }
\CSLRightInline{Müller, M. A. \emph{et al.} MERS coronavirus
neutralizing antibodies in camels, Eastern Africa, 1983--1997.
\emph{Emerging infectious diseases} \textbf{20}, 2093 (2014).}

\leavevmode\hypertarget{ref-Xu2004Epidemiologic}{}%
\CSLLeftMargin{38. }
\CSLRightInline{Xu, R.-H. \emph{et al.} Epidemiologic Clues to SARS
Origin in China. \emph{Emerging Infectious Diseases} \textbf{10},
1030--1037 (2004).}

\leavevmode\hypertarget{ref-Kasso2013Ecological}{}%
\CSLLeftMargin{39. }
\CSLRightInline{Kasso, M. \& Balakrishnan, M. Ecological and Economic
Importance of Bats (Order Chiroptera). \emph{ISRN Biodiversity}
\textbf{2013}, e187415 (2013).}

\leavevmode\hypertarget{ref-Voigt2016Bats}{}%
\CSLLeftMargin{40. }
\CSLRightInline{\emph{Bats in the Anthropocene: Conservation of Bats in
a Changing World}. (Springer International Publishing, 2016).
doi:\href{https://doi.org/10.1007/978-3-319-25220-9}{10.1007/978-3-319-25220-9}.}

\leavevmode\hypertarget{ref-Williams-Guillen2008Bats}{}%
\CSLLeftMargin{41. }
\CSLRightInline{Williams-Guillén, K., Perfecto, I. \& Vandermeer, J.
Bats Limit Insects in a Neotropical Agroforestry System. \emph{Science}
\textbf{320}, 70--70 (2008).}

\leavevmode\hypertarget{ref-Gonsalves2013Mosquito}{}%
\CSLLeftMargin{42. }
\CSLRightInline{Gonsalves, L., Bicknell, B., Law, B., Webb, C. \&
Monamy, V. Mosquito Consumption by Insectivorous Bats: Does Size Matter?
\emph{PLOS ONE} \textbf{8}, e77183 (2013).}

\leavevmode\hypertarget{ref-Gonsalves2013Mosquitoes}{}%
\CSLLeftMargin{43. }
\CSLRightInline{Gonsalves, L., Lamb, S., Webb, C., Law, B. \& Monamy, V.
Do mosquitoes influence bat activity in coastal habitats? \emph{Wildlife
Research} \textbf{40}, 10--24 (2013).}

\leavevmode\hypertarget{ref-Mello2011Missing}{}%
\CSLLeftMargin{44. }
\CSLRightInline{Mello, M. A. R. \emph{et al.} The Missing Part of Seed
Dispersal Networks: Structure and Robustness of Bat-Fruit Interactions.
\emph{PLOS ONE} \textbf{6}, e17395 (2011).}

\leavevmode\hypertarget{ref-Caraballo2022Crossspecies}{}%
\CSLLeftMargin{45. }
\CSLRightInline{Caraballo, D. A. Cross-Species Transmission of Bat
Coronaviruses in the Americas: Contrasting Patterns between
Alphacoronavirus and Betacoronavirus. \emph{Microbiology Spectrum}
\textbf{0}, e01411--22 (2022).}

\leavevmode\hypertarget{ref-Wu2021Comprehensive}{}%
\CSLLeftMargin{46. }
\CSLRightInline{Wu, Z. \emph{et al.} \emph{A comprehensive survey of bat
sarbecoviruses across China for the origin tracing of SARS-CoV and
SARS-CoV-2}. (2021)
doi:\href{https://doi.org/10.21203/rs.3.rs-885194/v1}{10.21203/rs.3.rs-885194/v1}.}

\leavevmode\hypertarget{ref-Carlson2022Climate}{}%
\CSLLeftMargin{47. }
\CSLRightInline{Carlson, C. J. \emph{et al.} Climate change increases
cross-species viral transmission risk. \emph{Nature} 1--1 (2022)
doi:\href{https://doi.org/10.1038/s41586-022-04788-w}{10.1038/s41586-022-04788-w}.}

\leavevmode\hypertarget{ref-Plowright2011Urban}{}%
\CSLLeftMargin{48. }
\CSLRightInline{Plowright, R. K. \emph{et al.} Urban habituation,
ecological connectivity and epidemic dampening: The emergence of hendra
virus from flying foxes (pteropus spp.). \emph{Proceedings of the Royal
Society B: Biological Sciences} \textbf{278}, 3703--3712 (2011).}

\leavevmode\hypertarget{ref-Alves2018Geographic}{}%
\CSLLeftMargin{49. }
\CSLRightInline{Alves, D. M. C. C., Diniz-Filho, J. A. F., da Silva e
Souza, K., Gouveia, S. F. \& Villalobos, F. Geographic variation in the
relationship between large-scale environmental determinants and bat
species richness. \emph{Basic and Applied Ecology} \textbf{27}, 1--8
(2018).}
